Rank Comparison

### 2023-11-30 Code/RankComparison.Rmd
Removed final chunk

The code below performs two clustered Wilcox tests, the first one without using
exact = TRUE, and the second one with exact = TRUE and 1,000,000 random
permutations. The tests compare the times and group by the Stage of the
competition, which in the data is coded as 1 if it was a national championship
and 2 if it was the world championships. The tests cluster by athlete, of which
for each dataset an integer from 1-11 is used (the values are arbitrary).
For more information about the "ds" method, please look at the Rank-based
Comparison subsection of the Methods section of the paper or at this link here:
https://www.jstatsoft.org/article/view/v096i06.

@@

The tests below are very similar to the ones above, the only difference being
grouping by Year instead of Stage (1 if 2019 and 2 if 2022).
```{r}
set.seed(1)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = old_clusrank,
                method = "ds")

@@

The tests below are very similar to the ones above, the only difference being
grouping by Year (2 if 2022 and 3 if 2023).
```{r}
set.seed(1)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = new_clusrank,
                method = "ds")

@@

The following code could be used to see what happens if we remove prelims. 
The sample sizes in the test become very small: 26 observations and 9 clusters.
```{r}
#nations_noprelim <- read.csv("../Data/Clusrank2019vs2022NoPrelims.csv")
#colnames(nations_noprelim) <- c("Time", "Athlete", "Year")
```

```{r}
#clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations_noprelim,
#                method = "ds")
#clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations_noprelim,
#                method = "ds", 
#                exact = TRUE, B = 10000)
```

>>>>

The code below performs two clustered Wilcox tests, the first one without using
exact = TRUE, and the second one with exact = TRUE and 1,000,000 random
permutations. The tests compare the times and group by the Stage of the
competition, which in the data is coded as 1 if it was a national championship
and 2 if it was the world championships. The tests cluster by athlete, of which
for each dataset an integer from 1-11 is used (the values are arbitrary).
For more information about the "ds" method, please look at the Rank-based
Comparison subsection of the Methods section of the paper or
[at this link here](https://www.jstatsoft.org/article/view/v096i06.)

@@

The tests below are very similar to the ones above, the only difference being
grouping by Year instead of Stage (0 if 2019 and 1 if 2022).
```{r}
set.seed(1)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = old_clusrank,
                method = "ds")

@@

The tests below are very similar to the ones above, the only difference being
grouping by Year (0 if 2022 and 1 if 2023).
```{r}
set.seed(1)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = new_clusrank,
                method = "ds")

@@
